SMT-Boosted Security Types for Low-Level MPC

### 2025-11-14 toplas26/examples.tex
checkpoint

We add coercions and typing assertions to the $\ttt{secopen}$ function
to specify properties of secure openings. After noninteractively
summing a wire value $\ttt{x}$ and a random Beaver triple value
$\ttt{x++a}$, the federation can publicly open the value since it is
masked by the random value. This is expressed using the coercion
$\ttt{as RECON(x) +  r[x++a]@3}$.

@@

In BDOZ a pre-processing phase is assumed where initial input secrets
are shared along with their associated MACs and keys. This can be
expressed in $\eqspre$ for input secrets $\sx{\ttt{"x"}}{1}$ and
$\sx{\ttt{"y"}}{2}$, for example, which subsume the following
constraints on shares:
{\footnotesize$$
\begin{array}{l}
\mx{\ttt{"xs"}}{2} \eop \sx{\ttt{"x"}}{1} \fminus \rx{\ttt{"x"}}{1} \wedge 
\mx{\ttt{"xs"}}{1} \eop \rx{\ttt{"x"}}{1} \wedge \\
\mx{\ttt{"ys"}}{1} \eop \sx{\ttt{"y"}}{2} \fminus \rx{\ttt{"y"}}{2} \wedge 
\mx{\ttt{"ys"}}{2} \eop \rx{\ttt{"y"}}{2} 
\end{array}
$$}
and the following constraint on keys and MACs for authentication
of $\sx{\ttt{"x"}}{1}$ (and similarly for $\sx{\ttt{"y"}}{2}$):
{\footnotesize$$
\begin{array}{l}
\mx{\ttt{"delta"}}{1} \eop \rx{\ttt{"delta"}}{1} \wedge
\mx{\ttt{"xk"}}{1} \eop \rx{\ttt{"xk"}}{1} \wedge\\
\mx{\ttt{"xm"}}{2} \eop \mx{\ttt{"xk"}}{1} \fplus (\mx{\ttt{"delta"}}{1} * \mx{\ttt{"xs"}}{2})
\end{array}
$$}
Given these global preconditions, a malicious secure opening of $\sx{\ttt{"x"}}{1} +
\sx{\ttt{"y"}}{2}$ would be obtained as
$\ttt{sum}(\ttt{"z"},\ttt{"x"},\ttt{"y"}); \ttt{open}(\ttt{"z"})$,
which type checks.

The definition of the $\ttt{mult}$ gate is presented in Figure
\ref{fig-bdozmult},
%where we present just client 1's side of the
%protocol $\ttt{\_mult1}$ (client 2's side is nearly symmetric but with
%a small variation-- refer to
%\cite{evans2018pragmatic,10.1007/978-3-030-68869-1_3} for more
%details).
%We could call this function on input secrets
%$\sx{\ttt{"x"}}{1}$ and $\sx{\ttt{"y"}}{2}$ in gate $\ttt{"g1"}$ as
%$\ttt{mult}(\ttt{"g1"},\ttt{"x"},\ttt{"y"})$, for example, or embed
%this gate internally in a circuit.
%
As for $\ttt{sum}$, the preconditions of $\ttt{mult}$ express
the expected MAC properties of input shares, as well as the
expected Beaver Triple property, and its postcondition
fexpresses the semi-homomorphic encryption property of
the resulting share, MAC, and key after gate execution-- specifically,
it preserves the BDOZ authentication property. Finally, the
postcondition of $\ttt{mult}$ expresses the
correctness property of the multiplication gate. In any case,
integrity of any circuit constructed from the $\ttt{sum}$ and
$\ttt{mult}$ library functions will require little SMT overhead
due to compositional verification, once their pre- and postconditions
are verified by type checking.

>>>>

We add coercions and typing assertions to the $\ttt{secopen}$ function
to specify properties of secure openings. After noninteractively
summing a wire value $\ttt{x}$ and a random Beaver triple value
$\ttt{x++a}$, the federation can publicly open the value since it is
masked by the random value. This is expressed using the coercion
$\ttt{as RECON(x) +  r[x++a]@3}$. The coercion then allows the
opened value to be declared $\ttt{public}$.

In the \ttt{mult} function, each client $\ttt{i}$ symmetrically
computes:
$$
\ttt{((m[z++"d"] * m[y]) + (-m[z++"e"] * m[z++"a"]) + m[z++"c"])@i}
$$
Since $\ttt{m[z++"d"]@i : public}$ and $\ttt{m[z++"e"]@i : public}$
are both established by $\ttt{secopen}$, and
$\ttt{m[y]@i}$, $\ttt{m[z++"a"]@i}$, and $\ttt{m[z++"c"]@i}$ are
all declared to be shares in preconditions, we have that each
of the shared computations $\ttt{(m[z++"d"] * m[y])@i}$ and $\ttt{(-m[z++"e"] * m[z++"a"])@i}$
are shares, so the gate outputs are shares, and this will
be successfully checked by syntax-directed $\Vdash$ type checking that
results from the declaration $\ttt{[m[z]@i1,m[z]@i2] : shares}$.

@@

Our Definition \ref{def-integrity} establishes a general semantics of
integrity, while the $\minicat$ integrity type system presented in
Section \ref{section-ipj} focuses on the use of BDOZ/SPDZ-style
MACs. A main concern here is the encorcement of MAC checking which is
an algebraic property. Here we show how pre and postconditions can be
used to enforce these properties in our arithmetic circuit library, in
Figure \ref{fig-beaver-bdoz}. Note that this code is an extension of the
library presented in Figure \ref{fig-beaver} and does not incorporate
the type annotations in Figure \ref{fig-beaver-types}, but this is
just for clarity of the presentation and these features could be combined.
